A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-29 UAM2014/Article/article.tex
la2pdf commit - 2014:04:29	12:41:09	(Tue29.Apr)

We have developed a simulator for synthetic aperture sonar (SAS) that creates object templates very quickly with the aid of the massive computing power in graphics processing units (GPUs). It uses OpenGL to render a optical 2D image and depth map of scene with a custom 3D model of the object and seafloor, and OpenCL to post-process this data to form sonar templates.

>>>>

We have developed a simulator for synthetic aperture sonar (SAS) that creates object templates very quickly with the aid of the massive computing power in graphics processing units (GPUs). It loads a 3D model of the sea floor and an object of interest into OpenGL, where emitted sound waves are modeled with a light source placed at the sonar transmit location. The backscattered sound intensity is assumed to follow a Lambertian model, i.e. only being dependent on incidence angle of the transmitted signal onto the model surface. After rendering OpenGL is set up to produce an optical 2D intensity image and a map of the distance from the propagation axis to each pixel in the image. This data is finally combined with OpenCL to produce the image templates.
